Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
fix spelling mistake

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated and substracted using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events ($N^{1\gamma}_{sim}$) to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we substracted
between 8 and 10\% of the data due to the $\pi^0$ contamination.

>>>>

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated and subtracted using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events ($N^{1\gamma}_{sim}$) to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we subtracted
between 8 and 10\% of the data due to the $\pi^0$ contamination.
